%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vishesh Agrawal} \\ \vspace{1pt}
    \small \href{mailto:agrawal.vishesh.178@gmail.com}{\underline{agrawal.vishesh.178@gmail.com}} $|$
    \href{https://github.com/awalvie}{\underline{github.com/awalvie}} $|$
    \href{https://awalvie.me/}{\underline{awalvie.me}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nirma University}{Ahmedabad, India}
      {Bachelor of Technology in Information Technology}{Jul. 2017 -- May 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SendX.io}{January 2021 -- Present}
      {Internship}{Remote}
      \resumeItemListStart
        \resumeItem{Setup monitoring for Sendpost.io from scratch using Prometheus, Grafana and various exporters.}
        \resumeItem{Wrote wrapper to push necessary metrics from the backend to Prometheus in Golang.}
        \resumeItem{Setup logging for Sendpost.io using Loki and Promtail.}
      \resumeItemListEnd

    \resumeSubheading
      {Major League Hacking}{October 2020 -- December 2020}
      {Open Source Fellow}{Remote}
      \resumeItemListStart
        \resumeItem{Contributed to Kiwi TCMS to increase code coverage in Django.}
		\resumeItem{Won the Halfway Hackthon, for project \href{https://github.com/zerefwayne/mlh-township}{"mlh-township"} in the "Best Community Project" category}
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Makera}{May. 2020-- Oct. 2020}
      {Backend Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Provision REST API routes using Flask.}
        \resumeItem{Used SQLAlchemy and Marshmallow to manage a PostgreSQL database.}
        \resumeItem{Deployed and managed production server for both the frontend and backend with NGINX.}
    \resumeItemListEnd

    \resumeSubheading
      {Inventum Pvt. Ltd.}{May. 2019 -- June. 2019}
      {Engineering Intern}{Noida, India}
      \resumeItemListStart
        \resumeItem{Built, compiled and configured an LFS (Linux From Scratch) distribution.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
	  \resumeProjectHeading
		  {\href{https://github.com/awalvie/anzibl}{\underline{\textbf{anzibl}}} $|$ \emph{Prometheus, Ansible, AWS EC2}}{December 2020}
		  \resumeItemListStart
			\resumeItem{Ansible project to automate provisioning and EC2 instance, deploy a webserver, monitor it using Prometheus and trigger alerts with alertmanager.}
		  \resumeItemListEnd
      \resumeProjectHeading
		  {\href{https://github.com/zerefwayne/mlh-township}{\underline{\textbf{mlh-township}}} $|$ \emph{NodeJS, WebSockets, WebRTC, PeerJS, React}}{November 2020}
          \resumeItemListStart
            \resumeItem{MLH Township harnesses the power of websockets and webRTC to provide the fellows a playgournd where they can comuunicate and hang out with each other in the game-like setting of MLH Town.}
			\resumeItem{Winner in the "Best Community Project" category for the MLH Halfway Hackthon.}
          \resumeItemListEnd
      \resumeProjectHeading
		  {\href{https://github.com/MLH-Fellowship/CovidAid}{\underline{\textbf{CovidAid}}} $|$ \emph{Flask, NGINX, PostgreSQL, SqlAlchemy}}{October 2020}
          \resumeItemListStart
            \resumeItem{A Hackathon Project made during our first week at MLH. I was resposbile for provisioning the backend, written in Flask, writing the core APIs, documenting the APIs and deploying it using NGINX.}
          \resumeItemListEnd
	  \resumeProjectHeading
		  {\href{https://github.com/awalvie/tengi}{\underline{\textbf{tengi}}} $|$ \emph{ANSI C}}{}
		  \resumeItemListStart
			\resumeItem{A minimal shell written in C. The goal with the project was to learn how a UNIX shell works and communicates with process and system calls.}
		  \resumeItemListEnd
	  \resumeProjectHeading
		  {\href{https://github.com/awalvie/lyceum}{\underline{\textbf{lyceum}}} $|$ \emph{ANSI C}}{}
		  \resumeItemListStart
			\resumeItem{A Static Site Generator, written with the primary goal of being simple and protable. The project uses no external libraries and build natively on any platform. It renders Text files with metadata about the file on top into plain HTML.}
		  \resumeItemListEnd
	  \resumeProjectHeading
		  {\href{https://github.com/awalvie/sersim}{\underline{\textbf{sersim}}} $|$ \emph{ANSI C}}{}
		  \resumeItemListStart
			\resumeItem{HTTP Server written in C to locally serve lyceum.}
		  \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, Golang} \\
     \textbf{Technologies}{: Django, Flask, Ansible, Prometheus, AWS, Beego} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, TMUX, Linux} \\
     \textbf{Familiar Languages}{: Bash, C++} \\
     \textbf{Familiar Technologies}{: Redis, WebSockets, WebRTC, OpenGL, SDL2} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
